Cocoa: Congestion Control Aware Queuing

### 2020-07-18 tex/paper.tex
Fix parameters in test.py

\def\tempYes{yes}
\def\tempNo{no}
\documentclass[sigconf, 10pt, letterpaper,dvipsnames\ifx\removeHeaders\tempYes ,nonacm\fi]{acmart}

@@

% Copyright
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\settopmatter{printacmref=false, printccs=false, printfolios=true}

% DOI
\acmDOI{}

% ISBN
\acmISBN{}

@@

%% {} with no args suppresses printing of the price
\acmPrice{}

\acmYear{2019}
\copyrightyear{2019}
\acmConference[BS'19]{Buffer Sizing Workshop}{December 2-3}{Stanford, CA}

>>>>

\def\tempYes{yes}
\def\tempNo{no}
\documentclass[sigconf, 10pt, letterpaper, dvipsnames\ifx\removeHeaders\tempYes ,nonacm\fi]{acmart}

@@

% Copyright
%\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

%\settopmatter{printacmref=false, printccs=false, printfolios=true}

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmlicensed}
\acmConference[BS '19]{2019 Workshop on Buffer Sizing}{December 2--3, 2019}{Palo Alto, CA, USA}
\acmBooktitle{2019 Workshop on Buffer Sizing (BS '19), December 2--3, 2019, Palo Alto, CA, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3375235.3375236}
\acmISBN{978-1-4503-7745-4/19/12}

@@

%% {} with no args suppresses printing of the price
%\acmPrice{}
%
%\acmYear{2019}
%\copyrightyear{2019}
%\acmConference[BS'19]{Buffer Sizing Workshop}{December 2-3}{Stanford, CA}
